Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-02-26 manuscript/manuscript.qmd
Update explanation for E2

We use the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility. While this is not a perfect measure---geographic scope is only one possible aspect of INGO operational space---it is an element of INGO flexibility that is directly influenced by China's ONGO law. Since INGOs are required to seek out separate PSUs for each province they are interested in working in, the count of authorized provinces partially reflects the alignment of INGO services with government preferences. Having a larger geographic scope provides concrete forms of INGO flexibility, like being able to more rapidly respond to changing needs in emergency situations such as the COVID-19 pandemic (e.g., a health-focused INGO can redirect staff to a province facing an outbreak), and allowing for a more diversified range of programs to assist with legal risk management when the definition of INGO activities is ambiguous (e.g., an INGO can pull back its work in a province if the relationship with its PSU sours). Previous work has shown that INGOs in China often work to maximize their geographic scope, even if they have no current plans to conduct activities nationwide. For instance, Oxfam and World Vision went through the cumbersome process to register multiple ROs to cover all the provinces they need to work in, and despite their goal of registering across mainland China, they faced increased bureaucratic hurdles and restriction with each registration [@Li:2020]. Based on @fig-theory, we posit that the alignment of government preferences and INGO services---represented by to contentiousness of an INGO's main issue area---helps determine INGO operational space. We thus expect that the number of provinces an organization is authorized to work in varies by INGO issue area:

@@

In cases where INGOs have a clear local-oriented focus, such as having a locality name in their registered RO purpose or names. Because they do not feel a need to go through the longer process of obtaining national-level registration. Accordingly, we temper our issue area expectation with a measure of explicitly local purpose. Organizations that have no intention of registering nationally should be registered in fewer provinces:

>>>>

We use the number of provinces an INGO is authorized to work in as a proxy for organizational flexibility. While this is not a perfect measure---geographic scope is only one possible aspect of INGO operational space---it is an element of INGO flexibility that is directly influenced by China's ONGO law. Since INGOs are required to seek out separate PSUs for each province they are interested in working in, the count of authorized provinces partially reflects the alignment of INGO services with government preferences. Having a larger geographic scope provides concrete forms of INGO flexibility, like being able to more rapidly respond to changing needs in emergency situations such as the COVID-19 pandemic (e.g., a health-focused INGO can redirect staff to a province facing an outbreak), and allowing for a more diversified range of programs to assist with legal risk management when the definition of INGO activities is ambiguous (e.g., an INGO can pull back its work in a province if the relationship with its PSU sours). Previous work has shown that INGOs in China often work to maximize their geographic scope, even if they have no current plans to conduct activities nationwide. For instance, Oxfam and World Vision went through the cumbersome process to register multiple ROs to cover all the provinces they might potentially work in, and despite their goal of registering across mainland China, they faced increased bureaucratic hurdles and restriction with each registration [@Li:2020]. Based on @fig-theory, we posit that the alignment of government preferences and INGO services---represented by to contentiousness of an INGO's main issue area---helps determine INGO operational space. We thus expect that the number of provinces an organization is authorized to work in varies by INGO issue area:

@@

As shown in @fig-theory, organization-level characteristics like internal preferences and resources are also determinants of INGO operational space. Since we measure organizational flexibility with a count of authorized provinces, we temper our expectations in E~1~ by analyzing organizational preferences related to geography. Not all INGOs seek to maximize their geographic reach. Organizations that explicitly limit their work to specific provinces or that work on issues that naturally lend themselves to a more limited scope (e.g., an INGO that supports educational services in one province) should be registered in fewer provinces:
